Thermodynamic response functions in a cell fluid model

### 2024-09-13 paper_text.tex
adjust references

\section{Introduction}
In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}. This model was used with the Morse potential in studies~\cite{KozlovskiiDobush2020,PylyukDobush2020} and with a modified Morse potential in~\cite{PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} as potentials describing the particle interaction. In particular, the equation of state was obtained in~\cite{KozlovskiiDobush2020} in the zero-mode approximation. This equation of state is used in the current work to calculate thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient.

@@

	\bibitem{HansenMcDonald2013} J.~Hansen, I.~McDonald. \textit{Theory of Simple Liquids: with Applications to Soft Matter} (Academic Press, 2013) [ISBN: 9780123870339]

>>>>

\section{Introduction}
In this work we continue our study of the thermodynamic behavior of a cell fluid model, which was defined in~\cite{KozitskyKozlovskiiDobush2018book,KozitskyKozlovskiiDobush2020}. This model was used with the Morse potential in studies~\cite{PylyukEtAlJML2023,PylyukKozlovskiiDobushUJP2023b} and with a modified Morse potential in~\cite{KozlovskiiDobush2020,PylyukDobush2020} as potentials describing the particle interaction. In particular, the equation of state was obtained in~\cite{KozlovskiiDobush2020} in the zero-mode approximation. This equation of state is used in the current work to calculate thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient.

@@

	\bibitem{HansenMcDonald2013} J.~Hansen, I.~McDonald. \textit{Theory of Simple Liquids: with Applications to Soft Matter.} 4th Edition (Academic Press, 2013) [ISBN: 9780123870339]
